Methodology for Assessing the State of the Practice for Domain X

### 2020-09-28 StateOfPractice/Methodology/Methodology.tex
updated section 4 of Methodology

\section{How to Identify the Domain} \label{SecIdentifyDomain}
\pmi{add introduction}
\pmi{add a definition in the introduction for what we mean by research software}
\begin{enumerate}	
	\item The domain must fall within the research software scope.
	\item The domain must be well understood.
	\item There must be a community of people studying the domain.
	\item A preliminary search, or discussion with experts, suggests that there will be numerous, at least about 15, candidate software packages to study.
	\item The software packages must have open source options. 
\end{enumerate}
\pmi{SS:"Add examples of well understood domains. We can include pointers to previous "state of the practice" projects as examples."}

>>>>

\section{How to Identify the Domain} \label{SecIdentifyDomain}
A domain of research software must be identified. Research software is defined in this exercise as ``software that is used to generate, process or analyze results that [are intended] to appear in a publication'' \citep{hettrick2014uk}. The chosen domain must have the following properties:

\begin{enumerate}	
	\item The domain must fall within the research software scope.
	\item The domain must be well understood.
	\item There must be a community of people studying the domain.
	\item A preliminary search, or discussion with experts, suggests that there will be numerous, at least about 15, candidate software packages to study.
	\item The software packages must have open source options. 
\end{enumerate}

Some examples of domains that fit these criteria are seismology software, as well as mesh generators and processors. These are described in \citep{SmithEtAl2018} and \citep{smith2016state}, respectively.
